---
title: "Mini Project Linear Regression"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Exercise: least squares regression

Use the /states.rds/ data set.

Fit a model predicting energy consumed per capita (energy) from the percentage of residents living in metropolitan areas (metro). 

Be sure to: 

  1. Examine/plot the data before fitting the model
  2. Print and interpret the model `summary'
  3. `plot' the model to look for deviations from modeling assumptions
  

###Load states.rds into a data frame and examine it's contents
```{r}
states <- readRDS("states.rds")
head(states)
```

###Examine and plot the data
```{r}
states.model1 <- subset(na.omit(states), select = c("metro", "energy"))
summary(states.model1)
plot(states.model1)
cor(states.model1)
```
**Metro and energy are not strongly correlated with a value of -.311**

###Print and interpret the model summary
```{r}
model1 <- lm(energy ~ metro, data = states.model1)
summary(model1)
```
**The P value for metro of .031 indicates it is a good predictor of energy, but with an R squared value of .078 there is a lot of error and not a good predictive model**

###Plot the model
```{r}
plot(model1)
```

###Select one or more additional predictors to add to your model and repeat steps 1-3.

###Add density and income to the model
```{r}
states.model2 <- subset(na.omit(states), select = c("metro", "density", "income", "energy"))
summary(states.model2)
plot(states.model2)
cor(states.model2)
```
**None of the variables are highly correlated with energy**

```{r}
model2 <- lm(energy ~ metro + density + income, data = states.model2)
summary(model2)
anova(model1, model2)
```
**In this model, none of the variables are good predictors of energy. Although our error has improved (0.077 - 0.149) it is still weak, and this is not a good model either. Based on the ANOVA test results, the second model is not significantly better than the first**


## Exercise: interactions and factors

Use the states data set.

##1. Add on to the regression equation that you created in exercise 1 by generating an interaction term and testing the interaction.

```{r}
model3 <- lm(energy ~ metro * density, data = states)
coef(summary(model3))
```
**None of these interactions appear to be significant**


##2. Try adding region to the model. Are there significant differences across the four regions?

```{r}
model4 <- lm(energy ~ metro * density + region, data = states)
anova(model4)
```
**There do not appear to be significant differences across regions**